Summary Tables

### 2021-05-18 injury_tables.Rmd

  #htmlwidgets::saveWidget(plotly::ggplotly(f), file.path(normalizePath(dirname(d)), basename(d)))
  #ggsave(f, file=paste0("results/multi_city/whw_matrices/whw_", cs,".png"), width = 14, height = 10, units = "cm")

@@

    el <- inner_join(el, td4, by = 'stage_mode')

@@

d <- ggplot(injury_risks_lng) +
  aes(x = stage_mode, fill = scenario, weight = value) +
  geom_bar(position = "dodge", colour = 'black') +
  scale_color_manual(values = cols) +
  scale_fill_discrete(guide = guide_legend(reverse=TRUE)) +
  coord_flip() +
  theme_minimal() +
  facet_wrap(vars(city)) +
  labs(x = "Strike Mode", y = "# of incidents", title = paste("Injury risk per billion km")) 
df <- injury_risks_lng %>% spread(value = value, key = city) 
df[df == 0] <- NA
df <- df %>% mutate(mv = rowMeans(select(., -c(stage_mode, scenario)))) %>% reshape2::melt()
df1 <- df %>% dplyr::filter(variable == 'mv')
df <- df %>% dplyr::filter(variable != 'mv')
d1 <- ggplot(df, aes(x = stage_mode, fill = variable, weight = value)) +
   geom_bar(position = "dodge", colour = 'black') +
   scale_fill_manual(values = cols_cbrewer) +
   theme_minimal() + 
   geom_point(data = df1, aes(x = stage_mode, fill = variable, y = value), colour = "black") + 
   facet_wrap(vars(scenario)) + 
   scale_y_continuous(breaks = seq(0, max(df$value, na.rm = T), 25)) +
   labs(x = "Strike Mode", y = "# of incidents", title = paste("Injury risk per billion km")) +
   theme(axis.text.x = element_text(face="bold", color="#993333", size=8, angle=90))
d2 <- ggplot(df %>% filter(!stage_mode %in% c('auto_rickshaw', 'bus', 'truck')), aes(x = stage_mode, fill = variable, weight = value)) +
    geom_bar(position = "dodge", colour = 'black') +
    scale_fill_manual(values = cols_cbrewer) +
    theme_minimal() + 
    geom_point(data = df1 %>% filter(!stage_mode %in% c('auto_rickshaw', 'bus', 'truck')) , aes(x = stage_mode, fill = variable, y = value), colour = "black") + 
    facet_grid(vars(scenario), scales='free_x') + 
    scale_y_continuous(breaks = seq(0, max(df$value, na.rm = T), 50)) +
    labs(x = "Strike Mode", y = "# of incidents", title = paste("Injury risk per billion km")) +
    theme(axis.text.x = element_text(face="bold", color="#993333", size=14))
# ggsave(d, file = paste0("results/multi_city/whw_matrices/plots/injury_risk_billion_km.png"), limitsize = F, dpi = 300, scale = 1.5)
fp <- paste0("results/multi_city/whw_matrices/interactive_plots/injury_risk_billion_km.html")
#htmlwidgets::saveWidget(plotly::ggplotly(d), file.path(normalizePath(dirname(fp)), basename(fp)))
# ggsave(d1, file = paste0("results/multi_city/whw_matrices/plots/injury_risk_billion_km_by_mode.png"),  width = 8, height = 5, dpi = 300, units = "in", scale = 2, device='png')
fp <- paste0("results/multi_city/whw_matrices/interactive_plots/injury_risk_billion_km_by_mode.html")
#htmlwidgets::saveWidget(plotly::ggplotly(d1), file.path(normalizePath(dirname(fp)), basename(fp)))
print(kable(format(injury_risks_b, scientific = F), caption = paste('Injury per billion km across all cities')))
fp <- paste0("results/multi_city/whw_matrices/interactive_plots/injury_risk_billion_km_by_specific_mode.html")
#htmlwidgets::saveWidget(plotly::ggplotly(d2), file.path(normalizePath(dirname(fp)), basename(fp)))
```

>>>>

  htmlwidgets::saveWidget(plotly::ggplotly(f), file.path(normalizePath(dirname(d)), basename(d)))
  #ggsave(f, file=paste0("results/multi_city/whw_matrices/whw_", cs,".png"), width = 14, height = 10, units = "cm")

@@

    el <- full_join(el, td4, by = 'stage_mode')

@@

d <- ggplot(injury_risks_lng) +
  aes(x = stage_mode, fill = scenario, weight = value) +
  geom_bar(position = "dodge", colour = 'black') +
  scale_color_manual(values = cols) +
  scale_fill_discrete(guide = guide_legend(reverse=TRUE)) +
  coord_flip() +
  theme_minimal() +
  facet_wrap(vars(city)) +
  labs(x = "Strike Mode", y = "# of incidents", title = paste("Injury risk per billion km")) 
df <- injury_risks_lng %>% spread(value = value, key = city) 
df[df == 0] <- NA
df <- df %>% mutate(mv = rowMeans(dplyr::select(., -c(stage_mode, scenario)))) %>% reshape2::melt()
df1 <- df %>% dplyr::filter(variable == 'mv')
df <- df %>% dplyr::filter(variable != 'mv')
d1 <- ggplot(df, aes(x = stage_mode, fill = variable, weight = value)) +
   geom_bar(position = "dodge", colour = 'black') +
   scale_fill_manual(values = cols_cbrewer) +
   theme_minimal() + 
   geom_point(data = df1, aes(x = stage_mode, fill = variable, y = value), colour = "black") + 
   facet_wrap(vars(scenario)) + 
   #scale_y_continuous(breaks = seq(0, max(df$value, na.rm = T), 25)) +
   labs(x = "Strike Mode", y = "# of incidents", title = paste("Injury risk per billion km")) +
   theme(axis.text.x = element_text(face="bold", color="#993333", size=8, angle=90))
d2 <- ggplot(df %>% filter(!stage_mode %in% c('auto_rickshaw', 'bus', 'truck')), aes(x = stage_mode, fill = variable, weight = value)) +
    geom_bar(position = "dodge", colour = 'black') +
    scale_fill_manual(values = cols_cbrewer) +
    theme_minimal() + 
    geom_point(data = df1 %>% filter(!stage_mode %in% c('auto_rickshaw', 'bus', 'truck')) , aes(x = stage_mode, fill = variable, y = value), colour = "black") + 
    facet_grid(vars(scenario), scales='free_x') + 
    # scale_y_continuous(breaks = seq(0, max(df$value, na.rm = T), 50)) +
    labs(x = "Strike Mode", y = "# of incidents", title = paste("Injury risk per billion km")) +
    theme(axis.text.x = element_text(face="bold", color="#993333", size=14))
# ggsave(d, file = paste0("results/multi_city/whw_matrices/plots/injury_risk_billion_km.png"), limitsize = F, dpi = 300, scale = 1.5)
fp <- paste0("results/multi_city/whw_matrices/interactive_plots/injury_risk_billion_km.html")
htmlwidgets::saveWidget(plotly::ggplotly(d), file.path(normalizePath(dirname(fp)), basename(fp)))
# ggsave(d1, file = paste0("results/multi_city/whw_matrices/plots/injury_risk_billion_km_by_mode.png"),  width = 8, height = 5, dpi = 300, units = "in", scale = 2, device='png')
 fp <- paste0("results/multi_city/whw_matrices/interactive_plots/injury_risk_billion_km_by_mode.html")
 htmlwidgets::saveWidget(plotly::ggplotly(d1), file.path(normalizePath(dirname(fp)), basename(fp)))
# print(kable(format(injury_risks_b, scientific = F), caption = paste('Injury per billion km across all cities')))
# ggsave(d2, file = paste0("results/multi_city/whw_matrices/plots/injury_risk_billion_km_by_specific_mode.png"), limitsize = F, dpi = 300, scale = 1.5)
fp <- paste0("results/multi_city/whw_matrices/interactive_plots/injury_risk_billion_km_by_specific_mode.html")
htmlwidgets::saveWidget(plotly::ggplotly(d2), file.path(normalizePath(dirname(fp)), basename(fp)))
```

### 2021-05-18 summary_tables.Rmd

@@

>>>>

|bangalore|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| pedestrian | 74.8|23.0|1.0 |
| cycle | 2.3|9.8|1.1 |
| car | 1.0|4.4|6.4 |
| motorcycle | 5.1|33.9|62.9 |
| bus | 15.1|24.3|24.9 |

|belo_horizonte|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| pedestrian | 89.1|8.6|0.3 |
| cycle | 1.6|2.7|0.2 |
| car | 7.3|65.1|43.9 |
| motorcycle | 1.3|10.1|5.0 |
| bus | 0.4|11.0|40.1 |

|bogota|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| pedestrian | 91.0|20.9|1.2 |
| cycle | 4.8|12.0|2.0 |
| car | 1.5|26.6|29.2 |
| motorcycle | 0.5|5.9|6.5 |
| bus | 0.8|20.6|56.7 |

|buenos_aires|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| pedestrian | 80.1|2.9|0.1 |
| cycle | 7.4|3.6|0.3 |
| car | 6.2|34.4|21.2 |
| motorcycle | 0.6|2.8|1.2 |
| bus | 3.5|50.0|50.7 |

|cape_town|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| pedestrian | 84.0|5.3|1.9 |
| cycle | 0.2|0.5|0.1 |
| car | 8.0|55.5|48.1 |
| motorcycle | 0.0|0.7|0.4 |
| bus | 6.9|34.8|33.1 |

@@

|mexico_city|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| pedestrian | 89.9|3.5|0.0 |
| cycle | 2.4|3.2|0.2 |
| car | 2.2|37.9|31.8 |
| motorcycle | 0.4|3.2|0.9 |
| bus | 1.7|34.8|33.8 |

|santiago|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| pedestrian | 84.0|3.9|0.0 |
| cycle | 6.2|6.1|0.5 |
| car | 8.1|58.7|32.3 |
| motorcycle | 0.1|2.2|1.1 |
| bus | 0.5|20.5|28.7 |

|sao_paulo|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| pedestrian | 82.6|1.9|0.0 |
| cycle | 1.3|1.4|0.1 |
| car | 12.6|65.2|36.8 |
| motorcycle | 0.8|3.1|1.9 |
| bus | 1.0|21.3|28.8 |

|vizag|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| pedestrian | 86.1|19.6|0.1 |
| cycle | 2.6|6.6|2.0 |
| car | 0.6|2.4|2.8 |
| motorcycle | 6.9|24.1|24.3 |
| bus | 0.8|26.7|54.8 |
